B_pilot_2

### 2018-08-30 experiments/B_pilot_2/writeup/B_pilot_2.Rmd
reompile for print

<style>
table, th, td {
    border: 1px grey;
    border-collapse: collapse;
    padding:2px 5px 2px 5px
}  
</style>

@@

<style>
table {
  white-space: nowrap;
}
</style>

```{r pander, echo=FALSE, cache=FALSE}
library(pander)
library(knitr)
```

```{r showInstructions, echo=FALSE, cache=TRUE}
v = c("crisp","vague")
e <- c("Choose the the square with many dots", "Choose the square with 20 dots")
i = data.frame(v, e)
names(i) = c("vagueness", "example instruction")
pander(i, justify=c('center', 'left'))
```

```{r showItems, echo=FALSE, cache=TRUE}
items = c(1,2,3,4,5,6,7,8)
i = data.frame(Gap = c("05","10","15","20"),
               x = c("25:20","25:15","25:10","25:05"),
               z = c("25:30","25:35","25:40","25:45") )
names(i) = c('Gap Size', 'Small Target', 'Large Target')
pander(i, justify=c('center', 'center', 'center'))
```

```{r loadLibraries, message=FALSE, echo=FALSE, cache=FALSE}
library(ggplot2); library(xtable); library(gridExtra); library(lme4); library(lmerTest);  library(data.table); library(dplyr); library(dtplyr); library(pander); library(LMERConvenienceFunctions); source('summarySEwithin2.R') 
```

```{r tidyr, echo=FALSE, message=FALSE}
library(tidyr)
```

```{r rawdata, cache=FALSE}
rawdata <- read.table('data.txt', sep=' ')
rawdata %>% head() %>% kable()
```

@@

```{r, results='asis', echo=F}
print(
  xtable(rtdataplot1,
         caption='Condition means'),
  include.rownames=FALSE,
  caption.placement='top',
  type='html')
```

```{r tableRTmodelSimple, results='asis', echo=FALSE, cache=TRUE}
x = as.data.frame(format(summary(rt.lmer.1)$coef, scientific=FALSE), stringsAsFactors = FALSE)

for (i in 1:(ncol(x)-1)) {
  for (j in 1:nrow(x)) {
    x[j,i] <-  substr(x[j,i], start=1, stop=7)
  }
}

for (i in 1:(ncol(x)-1)) {
  x[,i] <- as.numeric(x[,i])
}

for (i in ncol(x)) {
  for (j in 1:nrow(x)) {
    x[j,i] <-  substr(x[j,i], start=1, stop=7)
  }
}
print(
  xtable(
    align='lrrrrr', 
    digits=c(0, 2, 2, 1, 1, 3),
    x,
    caption="Response time model"), 
    caption.placement="top", 
  type='html')
```

@@

```{r erdataplot1, results='asis', echo=F}
print(
  xtable(erdataplot1,
         caption='Condition means'),
  include.rownames=FALSE,
  caption.placement='top',
  type='html')
```

```{r tableErrorModelsimple, results='asis', cache=TRUE, echo=FALSE}
print(
  xtable(
    summary(
    ac.lmer.1
    )$coefficients,
    digits=c(0, 2, 2, 2, 7), 
    caption="Error rates model"),
  caption.placement="top", type='html')
```

>>>>

<!-- <style> -->
<!-- table, th, td { -->
<!--     border: 1px grey; -->
<!--     border-collapse: collapse; -->
<!--     padding:2px 5px 2px 5px -->
<!-- }   -->
<!-- </style> -->

@@

<!-- <style> -->
<!-- table { -->
<!--   white-space: nowrap; -->
<!-- } -->
<!-- </style> -->

```{r pander, echo=FALSE, cache=FALSE, message=FALSE}
library(knitr)
library(tidyverse)
library(broom)
library(broom.mixed)
library(lme4)
library(lmerTest)
library(dotwhisker)
library(kableExtra)
library(LMERConvenienceFunctions)
library(data.table)
library(gridExtra)
source('summarySEwithin2.R')
source("B_pilot_2_functions/pretty_coef_table.R")
```

```{r showInstructions, echo=FALSE, cache=TRUE}
v = c("crisp","vague")
e <- c("Choose the the square with many dots", "Choose the square with 20 dots")
i = data.frame(Vagueness = v, Instruction = e)
kable(i) %>% kable_styling(full_width = F, position = "left", font_size = 11) 
```

```{r showItems, echo=FALSE, cache=TRUE}
items = c(1,2,3,4,5,6,7,8)
i = data.frame(Gap = c("05","10","15","20"),
               x = c("25:20","25:15","25:10","25:05"),
               z = c("25:30","25:35","25:40","25:45") )
names(i) = c('Gap Size', 'Small Target', 'Large Target')
kable(i) %>% kable_styling(full_width = F, position = "left", font_size = 11) 
```

```{r rawdata, cache=FALSE}
rawdata <- read.table('data.txt', sep=' ')
rawdata %>% head() 
```

@@

```{r, results='asis', echo=F}
kable(rtdataplot1, caption="condition means") %>% kable_styling(full_width = F, position = "left", font_size = 11) 
```

```{r tableRTmodelSimple, results='asis', echo=FALSE, cache=TRUE}
pretty_coef_table(rt.lmer.1, "rt.lmer.1")
```

@@

```{r erdataplot1, results='asis', echo=F}
kable(erdataplot1, caption="condition means") %>% kable_styling(full_width = F, position = "left", font_size = 11) 
```

```{r tableErrorModelsimple, results='asis', cache=TRUE, echo=FALSE}
pretty_coef_table(ac.lmer.1, "ac.lmer.1")
```
